Contextuality and the Born rule in fuzzy quantum theories

### 2017-03-15 prop_letter.tex
prop_letter.tex Updating BibLaTeX according to "biblatex-phys – A biblatex implementation of the aip and aps bibliography style"
prop_letter.tex Modifying according to "Physical Review Style and Notation Guide"...

\documentclass[reprint, aps, prl,superscriptaddress, showpacs,
showkeys]{revtex4-1} 
% Follow 
% https://tex.stackexchange.com/questions/37076/is-it-possible-to-load-biblatex-with-a-class-that-has-already-loaded-natbib/37077#37077
% to put RevTeX with BibLaTeX
\let\bibhang\relax
\let\citename\relax
\let\bibfont\relax
\let\Citeauthor\relax
\let\textcite\relax
\makeatletter
\DeclareRobustCommand{\MakeUppercase}[1]{{%
      \def\i{I}\def\j{J}%
      \def\reserved@a##1##2{\let##1##2\reserved@a}%
      \expandafter\reserved@a\@uclclist\reserved@b{\reserved@b\@gobble}%
      \protected@edef\reserved@a{\uppercase{#1}}%
      \reserved@a
   }}
\DeclareRobustCommand{\MakeLowercase}[1]{{%
      \def\reserved@a##1##2{\let##2##1\reserved@a}%
      \expandafter\reserved@a\@uclclist\reserved@b{\reserved@b\@gobble}%
      \protected@edef\reserved@a{\lowercase{#1}}%
      \reserved@a
   }}
\makeatother
\expandafter\let\csname ver@natbib.sty\endcsname\relax
\usepackage[ backend=biber,style=phys]{biblatex}
\addbibresource{prop.bib}
\ExecuteBibliographyOptions{sorting=none,maxbibnames=10,doi=false,isbn=false,url=false}
\usepackage{fullpage}
\usepackage[T1,T2A]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{mathrsfs}
\usepackage{bbold}
\usepackage{wesa}
\usepackage{graphicx}
\usepackage{verbatim}
\usepackage{hyperref}

@@

\title{Contextuality and the Born Rule in Fuzzy Quantum Theories}

@@

\date{\today }

\pacs{03.65.-w, 03.65.Ta, 02.40.Dr, 02.50.Cw, 02.50.Le}

\keywords{Finite precision measurement, the Born rule, Gleason's
theorem, interval-valued probability, discrete quantum theory}

\begin{abstract}
\begin{description}
\item[Background] This paper wants to understand the quantum measurement in the
bounded resource.
\item[Purpose] ?
\item[Method] We replace quantum real-valued probability measures by
interval-valued ones whose range can be restricted to finite number of
intervals representing finite precision measurement.
\item[Results] Quantum interval-valued probability measures provide a unified
framework to interpret the Kochen-Specker theorem and Gleason's theorem. We also
found some legitimate quantum interval-valued probability measures which cannot
be explained by the Born rule.
\item[Conclusions] Our research provide a new insight of the role of finite
precision measurement when formulate quantum theory.
\end{description}
\end{abstract}

>>>>

\documentclass[reprint, aps, prl,superscriptaddress, showpacs,
showkeys]{revtex4-1} 
% Follow 
% https://tex.stackexchange.com/questions/37076/is-it-possible-to-load-biblatex-with-a-class-that-has-already-loaded-natbib/37077#37077
% to put RevTeX with BibLaTeX
\let\bibhang\relax
\let\citename\relax
\let\bibfont\relax
\let\Citeauthor\relax
\let\textcite\relax
\makeatletter
\DeclareRobustCommand{\MakeUppercase}[1]{{%
      \def\i{I}\def\j{J}%
      \def\reserved@a##1##2{\let##1##2\reserved@a}%
      \expandafter\reserved@a\@uclclist\reserved@b{\reserved@b\@gobble}%
      \protected@edef\reserved@a{\uppercase{#1}}%
      \reserved@a
   }}
\DeclareRobustCommand{\MakeLowercase}[1]{{%
      \def\reserved@a##1##2{\let##2##1\reserved@a}%
      \expandafter\reserved@a\@uclclist\reserved@b{\reserved@b\@gobble}%
      \protected@edef\reserved@a{\lowercase{#1}}%
      \reserved@a
   }}
\makeatother
\expandafter\let\csname ver@natbib.sty\endcsname\relax
\usepackage[ backend=biber,style=phys,%
articletitle=false,biblabel=brackets,%
chaptertitle=false,pageranges=false%
]{biblatex}
\addbibresource{prop.bib}
\ExecuteBibliographyOptions{sorting=none,doi=false,isbn=false,url=false}
\usepackage{fullpage}
\usepackage[T1,T2A]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{mathrsfs}
\usepackage{bbold}
\usepackage{wesa}
\usepackage{graphicx}
\usepackage{verbatim}
\usepackage{hyperref}

@@

\title{Contextuality and the Born rule in fuzzy quantum theories}

@@

\date{\today}

\begin{abstract}
\begin{description}
\item[Background] In a world of bounded resource, any quantum measurement can
be only performed in finite precision.
\item[Method] We model idea of the finite precision measurement as finite number
of intervals, and the replace quantum real-valued probability measures by
interval-valued ones.
\item[Results] Quantum interval-valued probability measures provide a unified
framework to interpret the Kochen-Specker theorem and Gleason's theorem as
two limit cases. For the cases between them, we found some legitimate quantum
interval-valued probability measures which cannot be explained by the Born rule.
While restricting to only commuting projectors, the interval-valued probability
measures become classical, and these non-Born interval-valued probability
measures disappear.
\item[Conclusions] Our research provides a new insight of finite precision
measurement and non-commutativity when formulating quantum theory.
\end{description}
\end{abstract}

\pacs{03.65.Ta, 03.67.-a, 02.50.Cw, 02.50.Le}

\keywords{Finite precision measurement, the Born rule, Gleason's
theorem, the Kochen-Specker theorem, interval-valued probability measure,
discrete quantum theory}
